Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-22 paper.tex
Some content about compatibility

\subsection{Compatibility}

>>>>

While developing the novel DaaS platform, we faced multiple obstacles and challenges. Each of these issues belongs to one of the four categories: compatibility, performance, stability, and usability. This section presents the issues we were confronted with, the possible approaches we analyzed, and the solutions we chose.

\subsection{Compatibility}
% 
% TODO: Christian (1)
% TODO: Johannes (2)

The first relevant characteristic of a DaaS that a user is confronted with is the list of compatible applications. In the best case, all applications of all popular operating systems can be integrated and used with such a novel platform. Several DaaS projects and solutions from the last two decades, as well as similar concepts like web desktops or webtops, lacked native support for popular everyday applications.

Examples worth mentioning in this context is eyeOS (2005)~\cite{liu2012research}~\cite{vidyabanu2011implementation}, which simulated a desktop environment using HTML, PHP, JavaScript, and MySQL. Despite being open source, it has never become widely used since it is impossible to import and use native Windows or Linux applications with this software. All required applications have to be developed as web applications.

Kommerzielle Anwendungen...
